An exploratory analysis of the influence of resource use on the yield versus quality trade-off in Australian vineyards

### 2023-08-02 article.tex
Added highlights
fixed abstrat

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{An exploratory analysis of the influence of resource use on the yield versus quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
\affiliation[label1]{organization={QUT},
  addressline={},
  city={},
  postcode={},
  state={QLD},
  country={}}
\affiliation[label2]{organization={AWRI},
  addressline={},
  city={},
  postcode={},
  state={SA},
  country={}}
\affiliation[label3]{organization={Food Agility CRC},
  addressline={},
  city={},
  postcode={},
  state={Vic},
  country={}}
\author[label1,label2,label3]{Bryce Polley}
\date{20/06/2023}
\begin{abstract}
Using a ten year dataset that spans Australia we describe the relationships of input resources to the output yield and quality of grapes for wine production. Creating a baseline for comparing the efficiency of winegrowers with regard to the tradeoff between invested resources, yield and quality. Showing that economies of scale prevail for optimising crops for yield, with larger crops producing more grapes per area. And, showing that smaller crops utilising less resources are more closely related to quality.
\end{abstract}
%%Graphical abstract`
\begin{graphicalabstract}
  \includegraphics{graphical_abstract.jpeg}
\end{graphicalabstract}'

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC{} 0000 \sep{} 1111
\end{keyword}
%%Research highlights
\begin{highlights}
  \item Research highlight 1
  \item Research highlight 2
\end{highlights}
\end{frontmatter}

>>>>

\begin{document}
\begin{linenumbers}
\begin{frontmatter}
%% Title, authors and addresses
%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \affiliation for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%            addressline={}, 
%%            city={},
%%            postcode={}, 
%%            state={},
%%            country={}}
%% \fntext[label3]{}
\title{An exploratory analysis of the influence of resource use on the yield versus quality trade-off in Australian vineyards}
%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
\affiliation[label1]{organization={QUT},
  addressline={},
  city={},
  postcode={},
  state={QLD},
  country={}}
\affiliation[label2]{organization={AWRI},
  addressline={},
  city={},
  postcode={},
  state={SA},
  country={}}
\affiliation[label3]{organization={Food Agility CRC},
  addressline={},
  city={},
  postcode={},
  state={Vic},
  country={}}
\author[label1,label2,label3]{Author}
\date{20/06/2023}
\begin{abstract}
 The global focus on sustainability in agronomic industries has changed the way in which these enterprises do business. When strategies for a sustainable winegrowing industry are assessed, there is a trade-off between balancing the amount of resources invested and the resultant yield verses quality produced. In this analysis we observe relationships between yield and quality through the use of linear models. An extensive amount of research into a variety of factors' effect on grape quality and yield exists; but due to the lack of long-term and in-depth data, individual effects are often studied in isolation. The dataset used for this analysis includes data collected for the past 10 years from a multitude of vineyards located over a diverse range of Australian winegrowing regions. We aim to use this broad dataset to describe the relationship of input resources to the output yield and quality of vineyards. There was an expected strong relationship between size and resource use, with the overall space of a vineyard and its access to resources greatly determining the upper limit of potential yield. However, size was also negatively related to the potential quality, with higher quality being connected to high resource inputs per area; rather than to the overall expenditure of resources. Vineyard outputs were also augmented by regional and yearly affects. It is important to also consider a vineyard's business goal, region, external pressures and economies of scale. With regional constraints also contributing to deciding the best strategies to pursue when considering quality or quantity.  
\end{abstract}
%%Graphical abstract`
\begin{graphicalabstract}
  \includegraphics{graphical_abstract.jpeg}
\end{graphicalabstract}'

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Keyword one \sep{} keyword two
%% PACS codes here, in the form: \PACS code \sep code
\PACS{} 0000 \sep{} 1111
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC{} 0000 \sep{} 1111
\end{keyword}
%%Research highlights
\begin{highlights}
  \item Comparative analysis of resource use, quality and quantity in Australian winegrowing.
  \item Regional comparison of outcomes and resource use in Australian winegrowing regions.
  \item Baseline models for comparing wine crops.
  \item Analysis of national, decade long data source.
\end{highlights}
\end{frontmatter}
